---
title: "`r params$doc_title`"
date: "`r format(as.Date(params$date_of_valuation), '%B %e, %Y')`"
editor_options:
  chunk_output_type: console
output:
  officedown::rdocx_document:
    # toc: true
    # number_sections: true
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
        style: Table Caption
        pre: 'Table '
        sep: ': '
      conditional:
        first_row: true
        first_column: false
        last_row: false
        last_column: false
        no_hband: false
        no_vband: true
    page_size:
      width: 8
      height: 11
      orient: "portrait"
    page_margins:
      bottom: 1
      top: 1
      right: 1
      left: 1
      header: 0.5
      footer: 0.5
      gutter: 0.5 # What is gutter?
params:
  debug:
    input: checkbox
    label: Debug Mode
    value: true
  date_of_valuation:
    input: date
    label: Date of Valuation
    value: "2025-06-30"
  number_of_historical_years:
    input: numerical
    label: Number of historical years to show in the exhibits
    value: 2
  reporting_path:
    input: text
    label: Working directory for the monthly valuation process
    value:
  inputs_workbook:
    input: text
    label: Workbook Containing All Inputs Required for this process
    value: Data for Valuation.xlsx
  capital_workbook_pattern:
    input: text
    label: Pattern of the file naming convention for the workbook containing capital calls
    value: "Capital Model_Portfolio.*\\.xls"
  capital_worksheet_name:
    input: text
    label: Worksheet within the capital workbook containing capital calls
    value: "Agg_Report"
  capital_worksheet_range:
    input: text
    label: Range within the capital workbook worksheet containing capital calls
    value: "B24:BC337"
  doc_title:
    input: text
    label: Default title for the word document
    value: Portfolio & Capital Descriptions
---

```{r, setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = params$debug)
knitr::opts_knit$set(progress = TRUE, verbose = TRUE)

# Check if libraries are installed and load them
pacman::p_load("dplyr")

# prevent scientific notation for cross-platform compatibility
options(scipen = 999)

# As per our standards, we use environments for all local variables
local_env <- new.env()

# Document start time of code
local_env$time_begin <- Sys.time()
# local_env$subdirs <- list.dirs(path = params$reporting_path, full.names = TRUE, recursive = TRUE)
```

```{r, Localized Functions, echo=FALSE, include=FALSE}
# Returns the Excel range reference (e.g. cell addresses) of a named table in Excel
getRangeOfTable <- function(wb, sheet, name) {
  tables <- openxlsx::getTables(wb, sheet = sheet)
  attributes(tables[match(tables, name)])$names
}
```

```{r, get_portfolio_treaties, echo=FALSE, include=FALSE}
local_env$wb <- openxlsx::loadWorkbook(file.path(params$reporting_path, params$inputs_workbook))
# Import data and ensure strings aren't recognized as factors
local_env$treaty_positions <-
  readxl::read_excel(
    path = file.path(params$reporting_path, params$inputs_workbook),
    sheet = "Treaties",
    range = getRangeOfTable(wb = local_env$wb, sheet = "Treaties", "Treaties_Gold"),
    col_names = TRUE
  ) %>%
  rename(
    KEY = ConcatenatedKey,
  ) %>%
  mutate(
    EffectiveDate = as.Date(EffectiveDate), # openxlsx::convertToDate
    ExpirationDate = as.Date(ExpirationDate), # openxlsx::convertToDate
  )
```

# Table of Contents

```{r, table_of_contents, echo=FALSE}
officer::block_toc(level = 1)
```

# Risk Characteristics

Historical (pre-bind) data can be found for each portfolio can be found in the folder (Inforce Reporting).

Pre-bind actuarial review for each portfolio can be found in the folder (Underwriting).

The contracts supporting each live Protected Cell Company (PCC) can be found in the data room folder dedicated to PCC documentation (Contracts and Documentation/PCC Documents).

# Risk Concentration
```{r, get_largest_exposures, echo=FALSE}
# Determine the group by column "PrimaryLOB" with the largest sum of "TargetParticipation"
local_env$total_target_participation <- local_env$treaty_positions %>%
  summarise(TotalTargetParticipation = sum(TargetParticipation, na.rm = TRUE)) %>%
  pull(TotalTargetParticipation)

local_env$largest_lob <- local_env$treaty_positions %>%
  group_by(PrimaryLOB) %>%
  summarise(TotalTargetParticipation = sum(TargetParticipation, na.rm = TRUE)) %>%
  arrange(desc(TotalTargetParticipation)) %>%
  slice(1) %>%
  mutate(
    Percentage = TotalTargetParticipation / local_env$total_target_participation
  )

local_env$largest_carrier <- local_env$treaty_positions %>%
  group_by(Carrier) %>%
  summarise(TotalTargetParticipation = sum(TargetParticipation, na.rm = TRUE)) %>%
  arrange(desc(TotalTargetParticipation)) %>%
  slice(1) %>%
  mutate(
    Carrier = gsub("\\s*(\r?\n|\r)\\s*", " / ", Carrier) %>% gsub(" / / ", " / ", .),
    Percentage = TotalTargetParticipation / local_env$total_target_participation
  )
```

Our largest line of business by Gross Written Premium (GWP) is `r local_env$largest_lob$PrimaryLOB`,
which is projected to comprise approximately `r scales::percent(local_env$largest_lob$Percentage, accuracy=.01)` of our book.

Our largest counter party by GWP is `r local_env$largest_carrier$Carrier`,
which is projected to comprise approximately `r scales::percent(local_env$largest_carrier$Percentage, accuracy=.01)` of our book.

Both risk concentrations are projections, as each contract assumes a percentage of underwriting
risk for a given portfolio, with a cap on how much premium the cell will support.
Internally, we assume insurers will write 80% of their maximum authorization,
but deviations in actual underwriting by insurer will affect our actual risk concentration.

# Active Portfolios

```{r, list_portfolios, echo=FALSE, results='asis'}
local_env$distinct_names <- local_env$treaty_positions %>%
  distinct(Name) %>%
  arrange(Name) %>%
  pull(Name)

# Loop through each distinct name
for (name in local_env$distinct_names) {
  # Add subheading for the name; make sure this is one deaper than section above
  cat(sprintf("## %s\n", name))

  # Get distinct effective and expiration dates for the name
  local_env$date_ranges <- local_env$treaty_positions %>%
    filter(Name == name) %>%
    distinct(EffectiveDate, ExpirationDate) %>%
    arrange(EffectiveDate)

  # Print the date ranges
  local_env$sep <- "\n"
  local_env$indent <- ""
  if (nrow(local_env$date_ranges) > 1) {
    local_env$sep <- "  \n"
    local_env$indent <- "&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;" # Why HTML???
  }
  cat("Effective Dates:", local_env$sep)
  for (i in 1:nrow(local_env$date_ranges)) {
    cat(
      sprintf(
        "%s%s - %s%s",
        local_env$indent,
        format(as.Date(local_env$date_ranges$EffectiveDate[i]), "%B %e, %Y"),
        format(as.Date(local_env$date_ranges$ExpirationDate[i]), "%B %e, %Y"),
        "  \n"
      )
    )
  }

  # Get the first attachment type for the name
  # TODO: Can this ever vary by effective date?
  local_env$attachment <- local_env$treaty_positions %>%
    filter(Name == name) %>%
    select(RAvLOD) %>%
    slice(1) %>%
    mutate(RAvLOD = ifelse(RAvLOD == "LOD",
      "Losses Occurring During (Accident Date)",
      "Risk Attaching (Policy Issuance)"
    )) %>%
    pull(RAvLOD)

  # Print the narrative
  cat("Attachment: ", sprintf("%s  \n", local_env$attachment))

  # Get the first narrative for the name
  local_env$narrative <- local_env$treaty_positions %>%
    filter(Name == name) %>%
    select(Narrative) %>%
    slice(1) %>%
    pull(Narrative)

  # Print the narrative
  cat(sprintf("\n%s\n\n", local_env$narrative))
}
```

# Reinsurance
No reinsurance has been purchased by the PCCs to date, nor has any of the risk been retroceded, novated, or commuted.

<!---BLOCK_LANDSCAPE_START--->

# Capital Model
```{r, find_capital_model, echo=FALSE, include=FALSE, results='hide'}
# function to easy get the 3-char month and year of a date
format_date <- function(date) {
  format(as.Date(date), "%b %Y")
}

# Search for the file containing "Capital Call Model" in the specified directory
local_env$capital_call_file <- list.files(
  path = params$reporting_path,
  pattern = params$capital_workbook_pattern,
  recursive = FALSE,
  full.names = TRUE
)

# Check if the file exists https://readxl.tidyverse.org/reference/read_excel.html
if (length(local_env$capital_call_file) > 0) {
  local_env$capital_call_file_missing <- FALSE

  # Read the "Summary by Program" worksheet from the found file
  local_env$capital_model <- readxl::read_excel(
    local_env$capital_call_file[1],
    sheet = params$capital_worksheet_name,
    range = params$capital_worksheet_range,
    col_names = TRUE
    # skip = (params$capital_worksheet_firstrow - 1)
  )

  while (colnames(local_env$capital_model)[1] != "Carrier") {
    local_env$capital_model <- local_env$capital_model[, -1]
  }

  # Rename the first five columns
  colnames(local_env$capital_model)[1:6] <- c(
    "Carrier",
    "Program",
    "LineOfBusiness",
    "Bank",
    "Trust",
    "Measurement"
  )

  # Determine the first unnamed column index
  local_env$first_unnamed_column_index <- which(startsWith(colnames(local_env$capital_model), "..."))[1]

  # Remove the unnamed columns and any work done to the right of the data
  if (!is.na(local_env$first_unnamed_column_index)) {
    local_env$capital_model <- local_env$capital_model[
      ,
      -c(local_env$first_unnamed_column_index:ncol(local_env$capital_model))
    ]
  }

  # Remove the ...# piece at the end of any remaining columns
  colnames(local_env$capital_model) <- gsub("\\.\\.\\.[0-9]+$", "", colnames(local_env$capital_model))

  # Rename columns where the numeric value is greater than 2019-12-31 in Excel date format
  colnames(local_env$capital_model) <- sapply(colnames(local_env$capital_model), function(col) {
    if (!is.na(as.numeric(col)) && as.numeric(col) > as.numeric(as.Date("2019-12-31") - as.Date("1899-12-30"))) {
      as.character(openxlsx::convertToDate(as.numeric(col)))
    } else {
      col
    }
  })
} else {
  local_env$capital_call_file_missing <- TRUE
}
```

The full capital model can be found in the data room here: `r fs::path_rel(local_env$capital_call_file[1], params$reporting_path)`

## Capitalization To Date
Historical Collateral Calls (Periodic, not cumulative)
```{r, historic_capital_calls, echo=FALSE}
if (local_env$capital_call_file_missing == FALSE) {
  # calculate the current year and the cutoff year based on number_of_historical_years
  local_env$current_year <- as.numeric(format(as.Date(params$date_of_valuation), "%Y"))
  local_env$cutoff_year <- local_env$current_year - params$number_of_historical_years

  # Helper function to get quarter from a date string
  get_quarter <- function(date_str) {
    d <- as.Date(date_str)
    if (is.na(d)) {
      return(NA)
    }
    q <- paste0("Q", ceiling(as.numeric(format(d, "%m")) / 3))
    paste0(q, " ", format(d, "%Y"))
  }

  # Get all columns that are dates between cutoff_year-01-01 and date_of_valuation (inclusive)
  local_env$start_date <- as.Date(paste0(local_env$cutoff_year + 1, "-01-01"))
  local_env$end_date <- as.Date(params$date_of_valuation)
  local_env$period_columns <- colnames(local_env$capital_model)[
    sapply(colnames(local_env$capital_model), function(col) {
      tryCatch(
        {
          d <- as.Date(col)
          !is.na(d) && d >= local_env$start_date && d <= local_env$end_date
        },
        error = function(e) {
          FALSE
        }
      )
    })
  ]

  # Map each column to its quarter
  local_env$period_quarters <- sapply(local_env$period_columns, get_quarter)

  # Group columns by quarter
  local_env$quarter_groups <- split(local_env$period_columns, local_env$period_quarters)

  # Sort the quarters chronologically
  quarter_order <- names(local_env$quarter_groups)
  quarter_order <- quarter_order[!is.na(quarter_order)]
  quarter_df <- data.frame(
    quarter = as.integer(sub("Q([1-4]) .*", "\\1", quarter_order)),
    year = as.integer(sub(".* ([0-9]{4})$", "\\1", quarter_order)),
    name = quarter_order,
    stringsAsFactors = FALSE
  )
  quarter_df <- quarter_df[order(quarter_df$year, quarter_df$quarter), ]
  sorted_quarters <- quarter_df$name

  # For each quarter, sum the columns in that quarter
  local_env$historic_periodic_capital_calls <- local_env$capital_model %>%
    filter(Measurement == "Collateral Called [Periodic]") %>%
    filter(!Program %in% c("LOD", "Risk Attaching", "0")) %>%
    select(Program, LineOfBusiness, all_of(local_env$period_columns)) %>%
    mutate(across(all_of(local_env$period_columns), ~ as.numeric(gsub("[^0-9.-]", "", .))))

  for (q in sorted_quarters) {
    cols <- local_env$quarter_groups[[q]]
    if (length(cols) > 0) {
      local_env$historic_periodic_capital_calls[[q]] <- rowSums(local_env$historic_periodic_capital_calls[, cols, drop = FALSE], na.rm = TRUE)
    }
  }

  # Keep only Program, LineOfBusiness, and the new quarterly columns (sorted)
  local_env$historic_periodic_capital_calls <- local_env$historic_periodic_capital_calls %>%
    select(Program, LineOfBusiness, all_of(sorted_quarters))

  # Get all columns that are dates before or equal to the cutoff date
  local_env$cutoff_date <- as.Date(paste0(local_env$cutoff_year, "-12-31"))
  local_env$cutoff_columns <- colnames(local_env$capital_model)[
    sapply(colnames(local_env$capital_model), function(col) {
      tryCatch(
        {
          d <- as.Date(col)
          !is.na(d) && d <= local_env$cutoff_date
        },
        error = function(e) {
          FALSE
        }
      )
    })
  ]

  # Filter for cumulative collateral calls through the cutoff year
  local_env$historic_cumulative_capital_calls <- local_env$capital_model %>%
    filter(Measurement == "Collateral Called [Cumulative]") %>%
    filter(!Program %in% c("LOD", "Risk Attaching", "0")) %>%
    select(Program, LineOfBusiness, all_of(local_env$cutoff_columns)) %>%
    mutate(across(all_of(local_env$cutoff_columns), ~ as.numeric(gsub("[^0-9.-]", "", .))))

  # Use the last available cumulative column before or equal to cutoff date
  if (length(local_env$cutoff_columns) > 0) {
    last_col <- tail(local_env$cutoff_columns, 1)
    local_env$historic_cumulative_capital_calls$ThroughCutoff <- local_env$historic_cumulative_capital_calls[[last_col]]
  } else {
    local_env$historic_cumulative_capital_calls$ThroughCutoff <- NA
  }

  # Keep only Program, LineOfBusiness, and ThroughCutoff
  local_env$historic_cumulative_capital_calls <- local_env$historic_cumulative_capital_calls %>%
    select(Program, LineOfBusiness, ThroughCutoff)

  # Join the two tables on Program and add a total column
  local_env$historic_capital_calls <- local_env$historic_periodic_capital_calls %>%
    left_join(local_env$historic_cumulative_capital_calls, by = c("Program", "LineOfBusiness")) %>%
    select(Program, LineOfBusiness, ThroughCutoff, all_of(sorted_quarters)) %>%
    mutate(
      Total = rowSums(
        across(
          c(ThroughCutoff, all_of(sorted_quarters)),
          ~ as.numeric(gsub("[^0-9.-]", "", .))
        ),
        na.rm = TRUE
      ),
      across(
        c(ThroughCutoff, all_of(sorted_quarters), Total),
        \(x) scales::dollar(x, accuracy = 1, style_negative = "parens")
      ),
    ) %>%
    flextable::flextable()

  # Set header labels for quarters and ThroughCutoff
  local_env$historic_capital_calls <- flextable::set_header_labels(
    local_env$historic_capital_calls,
    values = setNames(sorted_quarters, sorted_quarters)
  ) %>%
    flextable::set_header_labels(
      values = c(ThroughCutoff = paste0("Through ", local_env$cutoff_year))
    )

  local_env$historic_capital_calls <- flextable::bold(local_env$historic_capital_calls, bold = TRUE, part = "header")
  local_env$historic_capital_calls <- flextable::fontsize(local_env$historic_capital_calls, size = 8, part = "all")
  local_env$historic_capital_calls <- flextable::font(local_env$historic_capital_calls, fontname = "Arial", part = "all")
  local_env$historic_capital_calls <- flextable::set_table_properties(local_env$historic_capital_calls, width = 1, layout = "autofit")
  local_env$historic_capital_calls <- flextable::bg(
    local_env$historic_capital_calls,
    i = which(
      tolower(local_env$historic_capital_calls$body$dataset$Program) %in%
        c("total bound", "projected")
    ),
    part = "body",
    bg = "#f0f0f0"
  )
  local_env$historic_capital_calls <- flextable::bg(
    local_env$historic_capital_calls,
    i = which(
      tolower(local_env$historic_capital_calls$body$dataset$Program) %in%
        c("total")
    ),
    part = "body",
    bg = "#e6e6e6"
  )

  # Knit the table into the document
  local_env$historic_capital_calls
} else {
  warning("Capital Call File Not Yet Available")
}
```

## Projected Future Capitalization Needs
Anticipated Collateral Calls (Periodic, not cumulative)
```{r, future_capital_calls, echo=FALSE}
if (local_env$capital_call_file_missing == FALSE) {
  # Get the columns for the remaining months of the current year through November of the next year
  local_env$next_year <- as.numeric(local_env$current_year) + 1
  local_env$next_years_columns <- colnames(local_env$capital_model)[
    sapply(colnames(local_env$capital_model), function(col) {
      tryCatch(
        {
          as.Date(col) > as.Date(params$date_of_valuation) &
            as.Date(col) <= as.Date(paste0(local_env$next_year, "-12-31"))
        },
        error = function(e) {
          FALSE
        }
      )
    })
  ]

  # Helper function to get quarter from a date string
  get_quarter <- function(date_str) {
    d <- as.Date(date_str)
    if (is.na(d)) {
      return(NA)
    }
    q <- paste0("Q", ceiling(as.numeric(format(d, "%m")) / 3))
    paste0(q, " ", format(d, "%Y"))
  }

  # Map each column to its quarter
  local_env$next_years_quarters <- sapply(local_env$next_years_columns, get_quarter)

  # Group columns by quarter
  local_env$quarter_groups <- split(local_env$next_years_columns, local_env$next_years_quarters)

  # Sort the quarters chronologically
  quarter_order <- names(local_env$quarter_groups)
  # Remove NA quarters if present
  quarter_order <- quarter_order[!is.na(quarter_order)]
  # Parse quarter and year for sorting
  quarter_df <- data.frame(
    quarter = as.integer(sub("Q([1-4]) .*", "\\1", quarter_order)),
    year = as.integer(sub(".* ([0-9]{4})$", "\\1", quarter_order)),
    name = quarter_order,
    stringsAsFactors = FALSE
  )
  quarter_df <- quarter_df[order(quarter_df$year, quarter_df$quarter), ]
  sorted_quarters <- quarter_df$name

  # Collapse monthly columns into quarterly sums
  local_env$projected_periodic_capital_calls <- local_env$capital_model %>%
    filter(Measurement == "Collateral Called [Periodic]") %>%
    filter(!Program %in% c("LOD", "Risk Attaching", "0")) %>%
    select(Program, LineOfBusiness, all_of(local_env$next_years_columns)) %>%
    mutate(across(all_of(local_env$next_years_columns), ~ as.numeric(gsub("[^0-9.-]", "", .))))

  for (q in sorted_quarters) {
    cols <- local_env$quarter_groups[[q]]
    if (length(cols) > 0) {
      local_env$projected_periodic_capital_calls[[q]] <- rowSums(local_env$projected_periodic_capital_calls[, cols, drop = FALSE], na.rm = TRUE)
    }
  }

  # Keep only Program, LineOfBusiness, and the new quarterly columns (sorted)
  local_env$projected_periodic_capital_calls <- local_env$projected_periodic_capital_calls %>%
    select(Program, LineOfBusiness, all_of(sorted_quarters))

  # Add a Total column
  local_env$projected_periodic_capital_calls <- local_env$projected_periodic_capital_calls %>%
    mutate(
      Total = rowSums(across(all_of(sorted_quarters)), na.rm = TRUE),
      across(
        c(all_of(sorted_quarters), Total),
        \(x) scales::dollar(x, accuracy = 1, style_negative = "parens")
      )
    ) %>%
    flextable::flextable()

  # Set header labels for quarters
  local_env$projected_periodic_capital_calls <- flextable::set_header_labels(
    local_env$projected_periodic_capital_calls,
    values = setNames(names(local_env$quarter_groups), names(local_env$quarter_groups))
  )

  local_env$projected_periodic_capital_calls <- flextable::bold(local_env$projected_periodic_capital_calls, bold = TRUE, part = "header")
  local_env$projected_periodic_capital_calls <- flextable::fontsize(local_env$projected_periodic_capital_calls, size = 8, part = "all")
  local_env$projected_periodic_capital_calls <- flextable::font(local_env$projected_periodic_capital_calls, fontname = "Arial", part = "all")
  local_env$projected_periodic_capital_calls <- flextable::set_table_properties(local_env$projected_periodic_capital_calls, width = 1, layout = "autofit")
  local_env$projected_periodic_capital_calls <- flextable::bg(
    local_env$projected_periodic_capital_calls,
    i = which(
      tolower(local_env$projected_periodic_capital_calls$body$dataset$Program) %in%
        c("total bound", "projected")
    ),
    part = "body",
    bg = "#f0f0f0"
  )
  local_env$projected_periodic_capital_calls <- flextable::bg(
    local_env$projected_periodic_capital_calls,
    i = which(
      tolower(local_env$projected_periodic_capital_calls$body$dataset$Program) %in%
        c("total")
    ),
    part = "body",
    bg = "#e6e6e6"
  )

  # Knit the table into the document
  local_env$projected_periodic_capital_calls
} else {
  warning("Capital Call File Not Yet Available")
}
officer::run_pagebreak()
```

# Transaction Terms


```{r, treaty_terms, echo=FALSE, results='asis'}
local_env$terms <- local_env$treaty_positions %>%
  arrange(Name, EffectiveDate) %>% # sort by Name and EffectiveDate
  rename(
    "Line of Business" = "PrimaryLOB",
    "Collateral Terms" = "CollateralTerms",
  ) %>%
  rowwise() %>%
  mutate(
    "Program" = paste0(Name, "  \n(", format_date(EffectiveDate), ")"),
    "Advantage / Differentiator" = Differentiator, # gsub("\\s*(\r?\n|\r)\\s*", "<br>", Differentiator),
    # "States" = gsub("\\s*(\r?\n|\r)\\s*", "<br>", States),
    # "Carrier" = gsub("\\s*(\r?\n|\r)\\s*", "<br>", Carrier),
    "Program Capacity" = scales::dollar(
      max(TotalSubjectPremium, 0),
      accuracy = 1,
      style_negative = "parens",
      scale_cut = scales::cut_short_scale()
    ),
    "Company Share" = scales::dollar(
      max(TargetParticipation, 0),
      accuracy = 1,
      style_negative = "parens",
      scale_cut = scales::cut_short_scale()
    ),
    # "Collateral Terms" = gsub("\\s*(\r?\n|\r)\\s*", "<br>", CollateralTerms),
    "Projected Loss Ratio" = scales::percent(LALAE.HalfImprovement.NetCorridorsAndCaps, accuracy = .01),
    "Projected Combined Ratio (includes all expense)" = scales::percent(CR.HalfImprovement, accuracy = .01)
  ) %>%
  ungroup() %>%
  select(
    Program,
    "Line of Business",
    "Advantage / Differentiator",
    States,
    Carrier,
    "Program Capacity",
    "Company Share",
    "Collateral Terms",
    "Projected Loss Ratio",
    "Commission & Risk Share",
    "Projected Combined Ratio (includes all expense)"
  ) %>%
  flextable::flextable()
# mutate(
#   Program = kableExtra::linebreak(Program, align = "c"),
#   States = kableExtra::linebreak(States, align = "c"),
#   Carrier = kableExtra::linebreak(Carrier, align = "c"),
#   "Collateral Terms" = kableExtra::linebreak(`Collateral Terms`, align = "c"),
#   "Commission & Risk Share" = kableExtra::linebreak(`Commission & Risk Share`, align = "c")
# ) %>%

# local_env$terms <- fontsize(local_env$terms, size = 12, part = "header")
local_env$terms <- flextable::bold(local_env$terms, bold = TRUE, part = "header")
local_env$terms <- flextable::fontsize(local_env$terms, size = 8, part = "all")
local_env$terms <- flextable::font(local_env$terms, fontname = "Arial", part = "all")
local_env$terms <- flextable::set_table_properties(local_env$terms, width = 1, layout = "autofit")
local_env$terms <- flextable::bg(
  local_env$terms,
  i = seq(1, nrow(local_env$terms$body$dataset), by = 2),
  part = "body",
  bg = "#f0f0f0"
)

# knitr::kable(escape = FALSE, format = "markdown")
local_env$terms
# without the stopping the landscape block, everything remains portrait
```
<!---BLOCK_LANDSCAPE_STOP--->
