---
title: "Portfolio & Capital Descriptions"
# This should be the valuation date though Sys.time()
date: "`r format(as.Date(params$date_of_valuation), '%B %e, %Y')`"
editor_options:
  chunk_output_type: console
output:
  officedown::rdocx_document:
    # toc: true
    # number_sections: true
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
        style: Table Caption
        pre: 'Table '
        sep: ': '
      conditional:
        first_row: true
        first_column: false
        last_row: false
        last_column: false
        no_hband: false
        no_vband: true
    page_size:
      width: 8
      height: 11
      orient: "portrait"
    page_margins:
      bottom: 1
      top: 1
      right: 1
      left: 1
      header: 0.5
      footer: 0.5
      gutter: 0.5 # What is gutter?
params:
  debug:
    input: checkbox
    label: Debug Mode
    value: true
  date_of_valuation:
    input: date
    label: Date of Valuation
    value: "2024-09-30"
  server_name:
    input: text
    label: Server Name
    value: ""
  server_port:
    input: numeric
    label: Port used to connect to server
    value: 1433
  user_name:
    input: text
    label: User Name
    value: ""
  password:
    input: text
    label: Password
    value: ""
  database_name:
    input: text
    label: Database containing treaty positions in the portfolio
    value: ""
  schema_name:
    input: text
    label: Schema containing treaty positions in the portfolio
    value: "dbo"
  table_name:
    input: text
    label: Table containing treaty positions in the portfolio
    value: ""
  reporting_path:
    input: text
    label: Working directory for the monthly valuation process
    value: ""
---

```{r, setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = params$debug)
knitr::opts_knit$set(progress = TRUE, verbose = TRUE)

# Check if libraries are installed and load them
pacman::p_load(
  DBI,
  odbc,
  dplyr,
  scales,
  readxl,
  officer,
  flextable
)

# prevent scientific notation for cross-platform compatibility
options(scipen = 999)

# As per our standards, we use environments for all local variables
local_env <- new.env()

# Document start time of code
local_env$time_begin <- Sys.time()
# local_env$subdirs <- list.dirs(path = params$reporting_path, full.names = TRUE, recursive = TRUE)
```

```{r, get_portfolio_treaties, echo=FALSE, include=FALSE}
# Connect to treaty positions database

# Create a connection string
local_env$con <- dbConnect(odbc::odbc(),
  Driver = "ODBC Driver 17 for SQL Server",
  Server = params$server_name,
  Port = params$server_port,
  Database = params$database_name,
  UID = params$user_name,
  PWD = params$password,
  Encrypt = "yes",
  TrustServerCertificate = "yes",
  Authentication = "SqlPassword"
)

# Query the table and store the result in local_env$treaty_positions
local_env$query <- sprintf(
  "SELECT * FROM %s.%s WHERE [EffectiveDate] IS NOT NULL AND
  COALESCE([TotalSubjectPremium], 0) > 0",
  params$schema_name,
  params$table_name
)
local_env$treaty_positions <- dbGetQuery(local_env$con, local_env$query)

# Close the connection
dbDisconnect(local_env$con)
```

## Table of Contents

```{r, table_of_contents, echo=FALSE}
block_toc()
```

## Risk Characteristics

Historical (pre-bind) data can be found for each portfolio can be found in the folder (Inforce Reporting).

Pre-bind actuarial review for each portfolio can be found in the folder (Underwriting).

The contracts supporting each live Protected Cell Company (PCC) can be found in the data room folder dedicated to PCC documentation (Contracts and Documentation/PCC Documents).

## Risk Concentration
```{r, get_largest_exposures, echo=FALSE}
# Determine the group by column "PrimaryLOB" with the largest sum of "TargetParticipation"
local_env$total_target_participation <- local_env$treaty_positions %>%
  summarise(TotalTargetParticipation = sum(TargetParticipation, na.rm = TRUE)) %>%
  pull(TotalTargetParticipation)

local_env$largest_lob <- local_env$treaty_positions %>%
  group_by(PrimaryLOB) %>%
  summarise(TotalTargetParticipation = sum(TargetParticipation, na.rm = TRUE)) %>%
  arrange(desc(TotalTargetParticipation)) %>%
  slice(1) %>%
  mutate(
    Percentage = TotalTargetParticipation / local_env$total_target_participation
  )

local_env$largest_carrier <- local_env$treaty_positions %>%
  group_by(Carrier) %>%
  summarise(TotalTargetParticipation = sum(TargetParticipation, na.rm = TRUE)) %>%
  arrange(desc(TotalTargetParticipation)) %>%
  slice(1) %>%
  mutate(
    Carrier = gsub("\\s*(\r?\n|\r)\\s*", " / ", Carrier) %>% gsub(" / / ", " / ", .),
    Percentage = TotalTargetParticipation / local_env$total_target_participation
  )
```

Our largest line of business by Gross Written Premium (GWP) is `r local_env$largest_lob$PrimaryLOB`,
which is projected to comprise approximately `r percent(local_env$largest_lob$Percentage, accuracy=.01)` of our book.

Our largest counter party by GWP is `r local_env$largest_carrier$Carrier`,
which is projected to comprise approximately `r percent(local_env$largest_carrier$Percentage, accuracy=.01)` of our book.

Both risk concentrations are projections, as each contract assumes a percentage of underwriting
risk for a given portfolio, with a cap on how much premium the cell will support.
Internally, we assume insurers will write 80% of their maximum authorization,
but deviations in actual underwriting by insurer will affect our actual risk concentration.

## Active Portfolios

```{r, list_portfolios, echo=FALSE, results='asis'}
local_env$distinct_names <- local_env$treaty_positions %>%
  distinct(Name) %>%
  arrange(Name) %>%
  pull(Name)

# Loop through each distinct name
for (name in local_env$distinct_names) {
  # Add subheading for the name; make sure this is one deaper than section above
  cat(sprintf("### %s\n", name))

  # Get distinct effective and expiration dates for the name
  local_env$date_ranges <- local_env$treaty_positions %>%
    filter(Name == name) %>%
    distinct(EffectiveDate, ExpirationDate) %>%
    arrange(EffectiveDate)

  # Print the date ranges
  local_env$sep <- "\n"
  local_env$indent <- ""
  if (nrow(local_env$date_ranges) > 1) {
    local_env$sep <- "  \n"
    local_env$indent <- "&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;" # Why HTML???
  }
  cat("Effective Dates:", local_env$sep)
  for (i in 1:nrow(local_env$date_ranges)) {
    cat(
      sprintf(
        "%s%s - %s%s",
        local_env$indent,
        format(as.Date(local_env$date_ranges$EffectiveDate[i]), "%B %e, %Y"),
        format(as.Date(local_env$date_ranges$ExpirationDate[i]), "%B %e, %Y"),
        "  \n"
      )
    )
  }

  # Get the first attachment type for the name
  # TODO: Can this ever vary by effective date?
  local_env$attachment <- local_env$treaty_positions %>%
    filter(Name == name) %>%
    select(RAvLOD) %>%
    slice(1) %>%
    mutate(RAvLOD = ifelse(RAvLOD == "RA",
      "Risk Attaching (Policy Issuance)",
      "Losses Occurring During (Accident Date)"
    )) %>%
    pull(RAvLOD)

  # Print the narrative
  cat("Attachment: ", sprintf("%s  \n", local_env$attachment))

  # Get the first narrative for the name
  local_env$narrative <- local_env$treaty_positions %>%
    filter(Name == name) %>%
    select(Narrative) %>%
    slice(1) %>%
    pull(Narrative)

  # Print the narrative
  cat(sprintf("\n%s\n\n", local_env$narrative))
}
```

## Reinsurance
No reinsurance has been purchased by the PCCs to date, nor has any of the risk been retroceded, novated, or commuted.

<!---BLOCK_LANDSCAPE_START--->

## Capital Model
```{r, find_capital_model, echo=FALSE, include=FALSE, results='hide'}
# Convert Excel serial date to date format
convert_excel_date <- function(excel_date) {
  as.Date(excel_date, origin = "1899-12-30")
}
# function to easy get the 3-char month and year of a date
format_date <- function(date) {
  format(as.Date(date), "%b %Y")
}

# Search for the file containing "Capital Call Model" in the specified directory
local_env$capital_call_file <- list.files(
  path = params$reporting_path,
  pattern = "Capital Call Model.*\\.xlsx$",
  recursive = FALSE,
  full.names = TRUE
)

# Check if the file exists
if (length(local_env$capital_call_file) > 0) {
  # Read the "Summary by Program" worksheet from the found file
  local_env$capital_model <- readxl::read_excel(
    local_env$capital_call_file[1],
    sheet = "Summary by Program",
    col_names = TRUE,
    skip = 3
  )

  # Rename the first five columns
  colnames(local_env$capital_model)[1:5] <- c("Carrier", "Program", "LineOfBusiness", "Bank", "DataColumns")

  # Determine the first unnamed column index
  local_env$first_unnamed_column_index <- which(startsWith(colnames(local_env$capital_model), "..."))[1]

  # Remove the unnamed columns and any work done to the right of the data
  local_env$capital_model <- local_env$capital_model[, -c(local_env$first_unnamed_column_index:ncol(local_env$capital_model))]

  # Remove the ...# piece at the end of any remaining columns
  colnames(local_env$capital_model) <- gsub("\\.\\.\\.[0-9]+$", "", colnames(local_env$capital_model))

  # Rename columns where the numeric value is greater than 2019-12-31 in Excel date format
  colnames(local_env$capital_model) <- sapply(colnames(local_env$capital_model), function(col) {
    if (!is.na(as.numeric(col)) && as.numeric(col) > as.numeric(as.Date("2019-12-31") - as.Date("1899-12-30"))) {
      as.character(convert_excel_date(as.numeric(col)))
    } else {
      col
    }
  })
} else {
  stop("Capital Call Model file not found in the specified directory.")
}
```

The full capital model can be found in the data room here: `r fs::path_rel(local_env$capital_call_file[1], params$reporting_path)`

### Capitalization To Date
Historical Collateral Calls (Periodic, not cumulative)
```{r, historic_capital_calls, echo=FALSE}
# calculate the current year, next year, and previous year
local_env$current_year <- format(as.Date(params$date_of_valuation), "%Y")
local_env$previous_year <- as.numeric(local_env$current_year) - 1

# Get the columns for the current year through the date of valuation
local_env$current_year_columns <- colnames(local_env$capital_model)[
  grepl(local_env$current_year, colnames(local_env$capital_model)) &
    sapply(colnames(local_env$capital_model), function(col) {
      tryCatch(
        {
          as.Date(col) <= as.Date(params$date_of_valuation)
        },
        error = function(e) {
          FALSE
        }
      )
    })
]

# Get the column from the year end preceding params$date_of_valuation
local_env$previous_year_column <- colnames(local_env$capital_model)[
  grepl(local_env$previous_year, colnames(local_env$capital_model)) &
    sapply(colnames(local_env$capital_model), function(col) {
      tryCatch(
        {
          as.Date(col) == as.Date(paste0(local_env$previous_year, "-12-31"))
        },
        error = function(e) {
          FALSE
        }
      )
    })
]

# Filter for periodic collateral calls in the current year
local_env$historic_periodic_capital_calls <- local_env$capital_model %>%
  filter(DataColumns == "Collateral Called [Periodic]") %>%
  filter(!Program %in% c("LOD", "Risk Attaching")) %>%
  select(Program, all_of(local_env$current_year_columns))

# Filter for cumulative collateral calls through the end of the previous year
local_env$historic_cumulative_capital_calls <- local_env$capital_model %>%
  filter(DataColumns == "Collateral Called [Cumulative]") %>%
  filter(!Program %in% c("LOD", "Risk Attaching")) %>%
  select(Program, all_of(local_env$previous_year_column))

# Join the two tables on Program and add a total column
local_env$historic_capital_calls <- local_env$historic_periodic_capital_calls %>%
  left_join(local_env$historic_cumulative_capital_calls, by = "Program") %>%
  select(Program, all_of(local_env$previous_year_column), all_of(local_env$current_year_columns)) %>%
  mutate(
    Total = rowSums(
      across(
        c(all_of(local_env$previous_year_column), all_of(local_env$current_year_columns)),
        ~ as.numeric(gsub("[^0-9.-]", "", .))
      )
    ),
    across(
      c(all_of(local_env$previous_year_column), all_of(local_env$current_year_columns), Total),
      \(x) scales::dollar(x, accuracy = 1, style_negative = "parens")
    ),
  ) %>%
  flextable::flextable()

# Create a named list with each date formatted
local_env$historic_capital_calls <- set_header_labels(
  local_env$historic_capital_calls,
  values = setNames(lapply(local_env$current_year_columns, format_date), local_env$current_year_columns)
) %>%
  set_header_labels(
    values = setNames(lapply(local_env$previous_year_column, function(col) {
      paste("Through", format(as.Date(col), "%Y"))
    }), local_env$previous_year_column)
  )

local_env$historic_capital_calls <- bold(local_env$historic_capital_calls, bold = TRUE, part = "header")
local_env$historic_capital_calls <- fontsize(local_env$historic_capital_calls, size = 8, part = "all")
local_env$historic_capital_calls <- font(local_env$historic_capital_calls, fontname = "Arial", part = "all")
local_env$historic_capital_calls <- set_table_properties(local_env$historic_capital_calls, width = 1, layout = "autofit")
local_env$historic_capital_calls <- bg(
  local_env$historic_capital_calls,
  i = which(
    tolower(local_env$historic_capital_calls$body$dataset$Program) %in%
      c("total bound", "projected")
  ),
  part = "body",
  bg = "#f0f0f0"
)
local_env$historic_capital_calls <- bg(
  local_env$historic_capital_calls,
  i = which(
    tolower(local_env$historic_capital_calls$body$dataset$Program) %in%
      c("total")
  ),
  part = "body",
  bg = "#e6e6e6"
)

# Knit the table into the document
# knitr::kable(local_env$historic_capital_calls)
local_env$historic_capital_calls
```

### Projected Future Capitalization Needs
Anticipated Collateral Calls (Periodic, not cumulative)
```{r, future_capital_calls, echo=FALSE}
# Get the columns for the remaining months of the current year through November of the next year
local_env$next_year <- as.numeric(local_env$current_year) + 1
local_env$next_years_columns <- colnames(local_env$capital_model)[
  sapply(colnames(local_env$capital_model), function(col) {
    tryCatch(
      {
        as.Date(col) > as.Date(params$date_of_valuation) &
          as.Date(col) <= as.Date(paste0(local_env$next_year, "-12-31"))
      },
      error = function(e) {
        FALSE
      }
    )
  })
]

# Get the column from the year end of the next year
local_env$next_year_end_column <- colnames(local_env$capital_model)[
  sapply(colnames(local_env$capital_model), function(col) {
    tryCatch(
      {
        as.Date(col) == as.Date(paste0(local_env$next_year, "-12-31"))
      },
      error = function(e) {
        FALSE
      }
    )
  })
]

# Filter for periodic collateral calls in prior to next calendar year end
local_env$projected_periodic_capital_calls <- local_env$capital_model %>%
  filter(DataColumns == "Collateral Called [Periodic]") %>%
  filter(!Program %in% c("LOD", "Risk Attaching")) %>%
  select(Program, all_of(local_env$next_years_columns))

# TODO: This may eventually be needed if we have more than one calendar year projected...
# Filter for cumulative collateral calls through the end of the projection less cumulative through the end of next calendar year
local_env$projected_cumulative_capital_calls <- local_env$capital_model %>%
  filter(DataColumns == "Collateral Called [Cumulative]") %>%
  filter(!Program %in% c("LOD", "Risk Attaching")) %>%
  select(Program, all_of(local_env$next_year_end_column))

local_env$projected_capital_calls <- local_env$projected_periodic_capital_calls %>%
  mutate(
    Total = rowSums(
      across(
        all_of(c(local_env$next_years_columns)),
        ~ as.numeric(gsub("[^0-9.-]", "", .))
      )
    ),
    across(
      c(all_of(local_env$next_years_columns), Total),
      \(x) scales::dollar(x, accuracy = 1, style_negative = "parens")
    ),
  ) %>%
  flextable::flextable()

local_env$projected_capital_calls <- set_header_labels(
  local_env$projected_capital_calls,
  values = setNames(lapply(local_env$next_years_columns, format_date), local_env$next_years_columns)
)

local_env$projected_capital_calls <- bold(local_env$projected_capital_calls, bold = TRUE, part = "header")
local_env$projected_capital_calls <- fontsize(local_env$projected_capital_calls, size = 8, part = "all")
local_env$projected_capital_calls <- font(local_env$projected_capital_calls, fontname = "Arial", part = "all")
local_env$projected_capital_calls <- set_table_properties(local_env$projected_capital_calls, width = 1, layout = "autofit")
local_env$projected_capital_calls <- bg(
  local_env$projected_capital_calls,
  i = which(
    tolower(local_env$projected_capital_calls$body$dataset$Program) %in%
      c("total bound", "projected")
  ),
  part = "body",
  bg = "#f0f0f0"
)
local_env$projected_capital_calls <- bg(
  local_env$projected_capital_calls,
  i = which(
    tolower(local_env$projected_capital_calls$body$dataset$Program) %in%
      c("total")
  ),
  part = "body",
  bg = "#e6e6e6"
)

# Knit the table into the document
# knitr::kable(local_env$projected_periodic_capital_calls)
local_env$projected_capital_calls
run_pagebreak()
```

## Transaction Terms


```{r, treaty_terms, echo=FALSE, results='asis'}
local_env$terms <- local_env$treaty_positions %>%
  arrange(Name, EffectiveDate) %>% # sort by Name and EffectiveDate
  rename(
    "Line of Business" = "PrimaryLOB",
    "Collateral Terms" = "CollateralTerms",
  ) %>%
  rowwise() %>%
  mutate(
    "Program" = paste0(Name, "  \n(", format_date(EffectiveDate), ")"),
    "Advantage / Differentiator" = Differentiator, # gsub("\\s*(\r?\n|\r)\\s*", "<br>", Differentiator),
    # "States" = gsub("\\s*(\r?\n|\r)\\s*", "<br>", States),
    # "Carrier" = gsub("\\s*(\r?\n|\r)\\s*", "<br>", Carrier),
    "Program Capacity" = scales::dollar(
      TotalSubjectPremium,
      accuracy = 1,
      style_negative = "parens",
      scale_cut = cut_short_scale()
    ),
    "Company Share" = scales::dollar(
      TargetParticipation,
      accuracy = 1,
      style_negative = "parens",
      scale_cut = cut_short_scale()
    ),
    # "Collateral Terms" = gsub("\\s*(\r?\n|\r)\\s*", "<br>", CollateralTerms),
    "Projected Loss Ratio" = scales::percent(PriorHalfImprovmentNetLALAERatio, accuracy = .01),
    "Commission & Risk Share" = {
      min_commission <- scales::percent(`MinimumCedingCommission`, accuracy = .01)
      min_lr <- scales::percent(`MinimumCedingCommissionLLAERatio`, accuracy = .01)
      prov_commission <- scales::percent(`ProvisionalCedingCommission`, accuracy = .01)
      prov_lr <- scales::percent(`ProvisionalCedingCommissionLLAERatio`, accuracy = .01)
      max_commission <- scales::percent(`MaximumCedingCommission`, accuracy = .01)
      max_lr <- scales::percent(`MaximumCedingCommissionLLAERatio`, accuracy = .01)
      # browser()

      if (min_commission == prov_commission && prov_commission == max_commission) {
        paste(sprintf("Flat: %s", min_commission))
      } else if (min_commission == prov_commission) {
        paste(
          sprintf("Min/Provisional: %s @ %s LR", min_commission, min_lr),
          sprintf("Max: %s @ %s LR", max_commission, max_lr),
          sep = "  \n"
        )
      } else if (prov_commission == max_commission) {
        paste(
          sprintf("Min: %s @ %s LR", min_commission, min_lr),
          sprintf("Provisional/Max: %s @ %s LR", prov_commission, prov_lr),
          sep = "  \n"
        )
      } else {
        paste(
          sprintf("Minimum: %s @ %s LR", min_commission, min_lr),
          sprintf("Provisional: %s @ %s LR", prov_commission, prov_lr),
          sprintf("Max: %s @ %s LR", max_commission, max_lr),
          sep = "  \n"
        )
      }
    },
    "Projected Combined Ratio (includes all expense)" = scales::percent(PriorHalfImprovementCombinedRatio, accuracy = .01)
  ) %>%
  ungroup() %>%
  select(
    Program,
    "Line of Business",
    "Advantage / Differentiator",
    States,
    Carrier,
    "Program Capacity",
    "Company Share",
    "Collateral Terms",
    "Projected Loss Ratio",
    "Commission & Risk Share",
    "Projected Combined Ratio (includes all expense)", "Commission & Risk Share"
  ) %>%
  flextable::flextable()
# mutate(
#   Program = kableExtra::linebreak(Program, align = "c"),
#   States = kableExtra::linebreak(States, align = "c"),
#   Carrier = kableExtra::linebreak(Carrier, align = "c"),
#   "Collateral Terms" = kableExtra::linebreak(`Collateral Terms`, align = "c"),
#   "Commission & Risk Share" = kableExtra::linebreak(`Commission & Risk Share`, align = "c")
# ) %>%

# local_env$terms <- fontsize(local_env$terms, size = 12, part = "header")
local_env$terms <- bold(local_env$terms, bold = TRUE, part = "header")
local_env$terms <- fontsize(local_env$terms, size = 8, part = "all")
local_env$terms <- font(local_env$terms, fontname = "Arial", part = "all")
local_env$terms <- set_table_properties(local_env$terms, width = 1, layout = "autofit")
local_env$terms <- bg(
  local_env$terms,
  i = seq(1, nrow(local_env$terms$body$dataset), by = 2),
  part = "body",
  bg = "#f0f0f0"
)

# knitr::kable(escape = FALSE, format = "markdown")
local_env$terms
# without the stopping the landscape block, everything remains portrait
```
<!---BLOCK_LANDSCAPE_STOP--->
